### 2017-03-05 Lab_4/solutions/L4-2-1.tex
Review of Lab_4, added refs to tracefiles where I saw they were missing. Fixed some typo's.
Former-commit-id: ff6b7c514b952aebc4a289413d0b6ba65828b4d6 [formerly 51435a56835d0eeb7babc90f9f0c25085709dd68 [formerly 51435a56835d0eeb7babc90f9f0c25085709dd68 [formerly 180a98254dcf255543ff72f101deac34a2312d85]]]
Former-commit-id: 69524c6d84a28ded87660ec5ba33aa32f5569b11
Former-commit-id: 06de46f32825fa1527f5d38c73593a2ba5a6a55f
Former-commit-id: b4ef786d70e62b66a72c3809b3ab492ea32a8df7

In the first dump, when the station sent an authentication frame (packet 2666) the AP replied with an authentication frame (packet 2668) indicating the station was succesfully authenticated (status code 0: successful).\\
In the second case, with MAC filtering enabled and configured to not allow STA1's wlan0 to connect,
the authentication frame(packet 464) sent by STA1 is met with an authentication frame(packet 466)
with status code 1. This indicates an unspecified failure. STA1 does not attempt an association as authentication failed. Note that STA1 is not informed that authentication failed because it was blacklisted. There is no reason to let a potential attacker know why exactly they could not connect.

>>>>

In the first dump (traces/L4-1-1.STA2.pcap), when the station sent an authentication frame (packet 2666) the AP replied with an authentication frame (packet 2668) indicating the station was succesfully authenticated (status code 0: successful).\\
In the second case (found in traces/L4-2-1.STA2.pcap), with MAC filtering enabled and configured to not allow STA1's wlan0 to connect,
the authentication frame(packet 464) sent by STA1 is met with an authentication frame(packet 466)
with status code 1. This indicates an unspecified failure. STA1 does not attempt an association as authentication failed. Note that STA1 is not informed that authentication failed because it was blacklisted. There is no reason to let a potential attacker know why exactly they could not connect.
